---
title: "arrival_rates"
author: "Eric"
date: "January 5, 2017"
output:
  pdf_document: default
  html_document: default
---
```{r, message=F, warning=F}
source("install_packages.R")
require(ggplot2)
require(dplyr)
require(magrittr)
require(tidyr)
require(lubridate)
d <- read.csv("callcenter_data_updated.csv")

# reshape countries to long form, format dates
d <- d %>% 
      gather(Country, callers, count_US:count_China) %>% 
      rename(date = DATE..MM.DD.YYYY, hour = HOUR, day = DAY, country = Country) %>% 
      mutate(date = as.Date(as.character(date), format = "%m/%d/%Y"),
             country = as.factor(country)) %>% 
      mutate(month = lubridate::month(date),
             day = lubridate::day(date),
             year = lubridate::year(date))

levels(d$country) <- substring(levels(d$country), first=7)  # correct country names
d$date_complete <- as.POSIXct(paste(d$date, d$hour), format="%Y-%m-%d %H")  # create date-hour feature
str(d)
```

### Stats for each country
```{r}
d2 <- spread(d, key=country, value=callers) %>% 
      select(China:US)

apply(d2, 2, mean)
apply(d2, 2, sd)
```


### By Country

One possibility would be to fit a ditribution to each country. For example, Germany and Turkey could be normal distributions with mean 25 and sd 3. India looks more like mean 5 and sd 1. But this doesn't account for peak times.

```{r}
ggplot(d) + geom_histogram(aes(x=callers), binwidth=1) + facet_grid(country ~ .) +
  ggtitle("Caller volume by country") + xlab("count of callers")
```

### Yearly cycle

Helper function for investigating caller cycles.
http://stackoverflow.com/questions/27975124/pass-arguments-to-dplyr-functionsr

```{r}
plot_caller_cycles <- function(cycle, granularity, country=TRUE, data=d){
  # takes groupby_vars as char vector of groupby terms

  groupby_vars <- c(cycle, granularity)
  if (country == T){
    groupby_vars <- c(groupby_vars, "country")
  }
  groupby_vars <- lapply(groupby_vars, as.symbol)
  
  temp <- data %>% 
          group_by_(.dots = groupby_vars) %>% # group_by_ to use standard eval
          summarise(callers = mean(callers))  # .dots to pass char vector as params
}

t <- plot_caller_cycles(cycle = "year", granularity = "day")

```


### Yearly cycle
```{r}
d %>% filter(country=="US") %>% 
  ggplot() + geom_line(aes(x=date_complete, y=callers)) + scale_x_datetime("2 days")
```

### Monthly cycle
```{r}

```

### Weekly cycle
```{r}
d %>% filter(country=="India") %>%  group_by(country, date, hour) %>% summarise(callers = mean(callers)) %>% 
  ggplot() + geom_line(aes(x=date, y=callers))
```

### Daily cycle
```{r}

```



